% !Mode:: "TeX:UTF-8" 

\begin{publication}
\noindent\textbf{（一）发表的学术论文}
\begin{publist}
\item \textbf{Yijia Liu}, Wanxiang Che, Yuxuan Wang, Bo Zheng, Bing Qin, and Ting Liu. Deep Contextualized Word Embeddings for Universal Dependency Parsing[J] // Transactions on Asian and Low-Resource Language Information Processing.（TALLIP，CCF~C类期刊，已录用待发表）
\item \textbf{Yijia Liu}, Wanxiang Che, Huaipeng Zhao, Bing Qin, and Ting Liu. Distilling Knowledge for Search-based Structured Prediction[C] // Proceedings of the 56th Annual Meeting of the Association for Computational Linguistics. 2018.（ACL，CCF~A类会议）
\item \textbf{Yijia Liu}, Wanxiang Che, Jiang Guo, Bing Qin, and Ting Liu. Exploring Segment Representations for Neural Segmentation Models[C] // Proceedings of 25th International Joint Conference on Artificial Intelligence. 2016.（IJCAI，CCF~A类会议）
\item \textbf{Yijia Liu}, Wanxiang Che, Bing Qin, and Ting Liu. HC-search for Incremental Parsing[C] // Proceedings of 25th International Joint Conference on Artificial Intelligence. 2016.（IJCAI，CCF~A类会议）
\item \textbf{Yijia Liu}, Wanxiang Che, Bo Zheng, Bing Qin, and Ting Liu.  An AMR Aligner Tuned by Transition-based Parser[C] // Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing. 2018.（EMNLP，CCF~B类会议）
\item \textbf{Yijia Liu}, Yue Zhang, Wanxiang Che, and Ting Liu. Domain Adaptation for CRF-based Chinese Word Segmentation using Free Annotations[C] // Proceedings of the 2014 Conference on Empirical Methods in Natural Language Processing. 2014.（EMNLP，CCF~B类会议）
\item \textbf{Yijia Liu}, Yi Zhu, Wanxiang Che, Bing Qin, Nathan Schneider, and Noah A. Smith. Parsing Tweets into Universal Dependency[C] // Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies. 2018.（NAACL，CCF~C类会议）
\item \textbf{Yijia Liu}, Yue Zhang, Wanxiang Che, and Ting Liu. Transition-Based Syntactic Linearization[C] // Proceedings of the 2015 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies. 2015. （NAACL，CCF~C类会议）
\item Yutai Hou, \textbf{Yijia Liu}, Wanxiang Che and Ting Liu, Sequence-to-Sequence Data Augmentation for Dialogue Language Understanding[C] // Proceedings of the 27th International Conference on Computational Linguistics. 2018.（COLING，CCF~B类会议）
\item Haoyang Wen, \textbf{Yijia Liu}, Wanxiang Che, Libo Qin and Ting Liu, Sequence-to-Sequence Learning for Task-oriented Dialogue with Dialogue State Representation[C] // Proceedings of the 27th International Conference on Computational Linguistics. 2018.（COLING，CCF~B类会议）
\end{publist}

\noindent\textbf{（二）申请及已获得的专利（无专利时此项不必列出）}
\begin{publist}
\item 车万翔、\textbf{刘一佳}、赵妍妍、刘挺.~一种中文分词增量学习方法：中国，CN201510604035.0[P]. 2015-11-18.
\end{publist}

\noindent\textbf{（三）参与的科研项目及获奖情况}
\begin{publist}
\item 刘挺、车万翔、胡郁、秦兵、陈毅恒、胡国平、张宇、赵妍妍、马汉君、张伟男、\textbf{刘一佳}.~语言技术平台及其应用. 黑龙江省科学技术一等奖. 2016.
\item Wanxiang Che, \textbf{Yijia Liu}, Yuxuan Wang, Bo Zheng, and Ting Liu. Towards Better UD Parsing: Deep Contextualized Word Embeddings, Ensemble, and Treebank Concatenation[C] // Proceedings of the CoNLL 2018 Shared Task: Multilingual Parsing from Raw Text to Universal Dependencies （CoNLL 2018通用多国语依存句法分析评测，LAS第一）
\end{publist}
%\vfill
%\hangafter=1\hangindent=2em\noindent
%\setlength{\parindent}{2em}
\end{publication}
